---
title: "mnist_R_Keras"
author: "Arun"
date: "April 22, 2018"
output: html_document
---

In this, we try to solve digit classification on mnist dataset using cnn.

Load package
```{r setup, include=FALSE}

library(keras)

```

Prepare the data

```{r}

batch_size <- 128
num_classes <- 10
epochs <- 12
```

Next, the dimensions of input image.
```{r}
img_rows <- 28
img_cols <- 28
```

The data is shuffled and split for training and testing.
```{r}
mnist <- dataset_mnist()
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y
```

Now, lets reshape the dimensions of data.
```{r}
x_train <- array_reshape(x_train, c(nrow(x_train), img_rows, img_cols, 1))
x_test <- array_reshape(x_test, c(nrow(x_test), img_rows, img_cols, 1))
input_shape <- c(img_rows, img_cols, 1)
```

Transform the rgb values into [0,1] range
```{r}
x_train <- x_train / 255
x_test <- x_test / 255

cat('x_train_shape:', dim(x_train), '\n')
cat(nrow(x_train), 'train samples\n')
cat(nrow(x_test), 'test samples\n')

```

Convert class vectors to binary class matrices
```{r}
y_train <- to_categorical(y_train, num_classes)
y_test <- to_categorical(y_test, num_classes)
```

Lets' define the model in keras

```{r}
# Define model
model <- keras_model_sequential() %>%
  layer_conv_2d(filters = 32, kernel_size = c(3,3), activation = 'relu',
                input_shape = input_shape) %>% 
  layer_conv_2d(filters = 64, kernel_size = c(3,3), activation = 'relu') %>% 
  layer_max_pooling_2d(pool_size = c(2, 2)) %>% 
  layer_dropout(rate = 0.25) %>% 
  layer_flatten() %>% 
  layer_dense(units = 128, activation = 'relu') %>% 
  layer_dropout(rate = 0.5) %>% 
  layer_dense(units = num_classes, activation = 'softmax')

```

Next, we compile the model
```{r}
# Compile model
model %>% compile(
  loss = loss_categorical_crossentropy,
  optimizer = optimizer_adadelta(),
  metrics = c('accuracy')
)

```

Now, lets train it on the training set.
```{r}
# Train model
model %>% fit(
  x_train, y_train,
  batch_size = batch_size,
  epochs = epochs,
  validation_split = 0.2
)

```

Finally, we display the accuracy of the model on test dataset.
```{r}
scores <- model %>% evaluate(
  x_test, y_test, verbose = 0
)

# Output metrics
cat('Test loss:', scores[[1]], '\n')
cat('Test accuracy:', scores[[2]], '\n')
```

